Multisensor Architecture for an Intersection Management System

### 2018-01-23 ch3-arch_sys.tex
Restructured chapter 3 and added redis reference to bib

% Architecture Description and system specifications
% 	* Multisensor IMS		
%		* Processing Stages
%		* Fusion approaches
%		* Methods and techniques
%		* Architecture proposal
%	* Validation approaches
%		* Transportation and Traffic Simulations
%			* Simulators Classification
%		* Intersection monitoring Datasets
%			* POSSi Dataset
%			* KoPER Dataset

@@

Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors manufacturing and computing capabilities. Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control step. Also it is needed to test and validate the developments prior to a real and full functional implementation. The first part of this chapter describes the main stages in a intersection management system based on image and range sensors, and the methods used in these stages. Then an architecture proposal for the implementation of such a system is presented. Finally, two validation tools for IMS applications are described, simulation models and datasets.

@@

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene. Spatial-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, and also is shown how the data volume is reduced while data meaning increases in the last stages.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{fig/3/proc_stages.png}
\caption{Dataflow through processing stages in an IMS.}
\label{proc_stages}
\end{figure}

@@

Depending on system design, if it has multiple sensors of the same type or different type, a data fusion approach should be chosen. When data came from same-type sensors, it is usually fused at low levels using techniques for temporal-spatial alignment, depending on sensors configuration. This is the case for a network of lasers or lidars or for multi-camera systems. If the system have different type of sensors, data from them may be fused at mid level, based on extracted features or classes on each subsystem; or may be fused at high level if each subsystem delivers control or decision outputs.

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{fig/3/processing_stages_and_tasks.png}
\caption{Processing stages and tasks performed.}
\label{proc_stages_tasks}
\end{figure}

\subsection{Preprocessing}
\subsubsection{Time-space alignment}
\subsubsection{Background subtraction}
\subsubsection{Filtering}
\subsection{Feature analysis}
\subsubsection{Segmentation}
\subsubsection{Feature extraction}
\subsubsection{Feature selection}
\subsection{Pattern recognition}
\subsubsection{Object association}
\subsubsection{Object tracking}
\subsubsection{Object classification}
\subsection{Situation assessment}

@@

>>>>

% Architecture Description and system specifications
% 	* Multisensor IMS		
%		* Processing Stages
%		* Fusion approaches		
%	* Validation approaches
%		* Transportation and Traffic Simulations
%			* Simulators Classification
%		* Intersection monitoring Datasets
%			* POSSi Dataset
%			* KoPER Dataset
%	* Architecture proposal

@@

Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors manufacturing and computing capabilities. Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control step. It is also needed to test and validate the developments prior to a real and full functional implementation. The first part of this chapter describes the main stages in a intersection management system based on image and range sensors, and the methods used in these stages. Then an architecture proposal for the implementation of such a system is presented. Finally, two validation tools for IMS applications are described, simulation models and datasets.

@@

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene. Spatial-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, including common task performed at each of these stage and also is shown how the data volume is reduced while data meaning increases in the last stages.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{fig/3/processing_stages_and_tasks.png}
\caption{Dataflow through processing stages in an IMS an commonly performed tasks}
\label{proc_stages}
\end{figure}

@@

Depending on wheter the system has multiple sensors of the same type or different type, a data fusion approach should be chosen. When data came from same-type sensors, it is usually fused at low levels using techniques for temporal-spatial alignment, depending on sensors configuration. This is the case for a network of lasers or lidars or for multi-camera systems. If the system have different type of sensors, data from them may be fused at mid level, based on extracted features or classes on each subsystem; or may be fused at high level if each subsystem delivers control or decision outputs. The tasks shown in each of the processing stages (\ref{proc_stages}), could be used as fusion blocks for homogeneous or heterogeneous data.

@@

@@

The proposal presented in this work is based on MFI model processing entities in the sense that a processing block could take one or more inputs related between them and generate an output of the same type or a higher level output. The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from.

\subsection{Data Model}

\subsection{Communication scheme}

In order to isolate the processing tasks of the communication system, a Publisher-Subscriber approach is selected. The benefits of this option is that data can be shared between diferent blocks without generating a dependency from publishers to subscribers. Another benefit is that exposing a defined mechanism for publishing or subscribing, allows the system to be implementation agnostic.

Taking these reasons into account, Redis is chosen as communication platform. As stated in their website, "Redis is an open source (BSD licensed), in-memory data structure store, used as a database, cache and message broker"\cite{Redis} which support Publisher-Subscriber paradigm, allowing greater scalability and a more dynamic network topology.

\subsection{Processing Blocks}
